

\section{Example Section}

This is a section where basic commands are shown

Just look at the \ic{examples/examples.Tex} file.

\subsection{Example Subsection}

Some commands are following\ldots

\subsubsection{General Text Formatting}

\emph{Emphasize}, \textbf{bold}, 

\subsubsection{Lists}

Unordered list:
\begin{itemize}
    \item some list item
    \item and another
\end{itemize}

Enumerated list:
\begin{enumerate}
    \item first item
    \item and the second one
\end{enumerate}

\subsubsection{Text referencing}

Every time you use a \ic{label} you can reference it by using the \ic{ref} command.
I've created some custom commands that handle labels and referencing more implicitly for images and code.

Just ask for details.

\subsubsection{Maths}

Inline math is as easy as $1 + 1 = 2$, you see?

\topic{Centered Equation}
\[
    1 + 1 = 2
\]

\topic{Numbered (and referencable) Equation}
\begin{equation}
    1 + 1 = 2
    \label{eq:equation-reference-id}
\end{equation}

I can use the \ic{ref} command to reference equation (\ref{eq:equation-reference-id}).


\subsubsection{Code}
There are three variants to insert code. The visuals could be tweaked.

\topic{Inline Code}
The first is \ic{inline code}, where just a monospace font is used.

\topic{Code environment}
This Code is directly written inside an lstlisting environment:
\begin{lstlisting}
function one(){
    return 1;
}
\end{lstlisting}

\begin{minipage}{\textwidth}{
\topic{Code from file}
\emph{Note:} The minipage environment can be used to prevent code being split by a page break.
        \code{Example code inserted from examples/code.js}{examples/code.js}{code-reference-id}
}
\end{minipage}


\subsubsection{Footnotes}

A footnote\footnote{some explanatory text} is created with the footnote command.


\subsubsection{Citations}
We still have to figure out how to go about a shared bibliography.
My Mendeley creates a bibliography for the DME references automatically.
We could use this as a basis and have additional .bib files for individual references.

Anyways\ldots I'd like to cite Millán \cite{Millan2004} in here.

